An Efficient Audio Coding Scheme for Quantitative and Qualitative Large Scale Acoustic Monitoring Using the Sensor Grid Approach

### 2018-12-05 paper/articleV3.tex
Add correct python implementation

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad {LS2N}{, UMR 6004, CNRS, \'Ecole Centrale de Nantes, 44300 Nantes}, France; felix.gontier@ls2n.fr\\%please add the complete location and add its zip code. %R: done
$^{2}$ \quad {IFSTTAR, AME, LAE}{, 44340 Bouguenais, France}; pierre.aumond@ifsttar.fr (P.A.); arnaud.can@ifsttar.fr (A.C.)\\%please add the complete location and add it's zip code. %R: done
$^{3}$ \quad {ETIS, UMR 8051}%please add the complete location and add it's zip code.
, Universit\'e Paris Seine, Universit\'e de Cergy-Pontoise, ENSEA, CNRS, F-95000 {Cergy-Pontoise}; %please add the city. %R: done
 catherine.lavandier@u-cergy.fr}

@@

\conflictsofinterest{The authors declare no conflict of interest.}%Please disclose conflicts of interest, or add 'The authors declare no conflicts of interest'. %R: No conflicts of interest
%=====================================
% References, variant B: external bibliography
%=====================================
\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}
\section{References}
\begin{thebibliography}{999}
\providecommand{\natexlab}[1]{#1}

>>>>

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad {LS2N, UMR 6004, \'Ecole Centrale de Nantes, 44300 Nantes, France}, France; felix.gontier@ls2n.fr\\%please add the complete location and add its zip code. %R: done
$^{2}$ \quad {LAE, AME, IFSTTAR, 44340 Bouguenais, France}; pierre.aumond@ifsttar.fr (P.A.); arnaud.can@ifsttar.fr (A.C.)\\%please add the complete location and add it's zip code. %R: done
$^{3}$ \quad {ETIS, UMR 8051, Université Paris Seine, Université de Cergy-Pontoise, ENSEA, CNRS, 95000 Cergy-Pontoise, France}; %please add the city. %R: done
 catherine.lavandier@u-cergy.fr}

@@

\conflictsofinterest{The authors declare no conflict of interest.}%Please disclose conflicts of interest, or add 'The authors declare no conflicts of interest'. %R: No conflicts of interest
%=====================================
% References, variant B: external bibliography
%=====================================
\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}
\reftitle{References}
\begin{thebibliography}{999}
\providecommand{\natexlab}[1]{#1}
